Measuring the Type Ia supernova delay time distribution via host galaxy rates in the Dark Energy Survey

### 2021-01-20 draft.tex

All software used in this publication is publicly available. In particular, we made extensive use of \texttt{numpy} \citep{Harris2020}, \texttt{Astropy} \citep{Price-Whelan2018}, \texttt{matplotlib} \citep{Hunter2007}, \texttt{SciPy} \citep{Virtanen2020}, \texttt{pandas} \citep{Mckinney2010}, \texttt{Stan} \citep{Carpenter2017}, \texttt{seaborn}, and \texttt{arviz} \citep{Kumar2019}.

>>>>

All software used in this publication is publicly available. In particular, we made extensive use of \texttt{numpy} \citep{Harris2020}, \texttt{Astropy} \citep{AstropyCollaboration2013,AstropyCollaboration2018}, \texttt{matplotlib} \citep{Hunter2007}, \texttt{SciPy} \citep{Virtanen2020}, \texttt{pandas} \citep{Mckinney2010}, \texttt{Stan} \citep{Carpenter2017}, \texttt{seaborn} \citep{Waskom2020}, and \texttt{arviz} \citep{Kumar2019}.
